Environmental factors affecting Galaxy Morphology

### 2014-07-27 Writeup/paper_v2.tex
add environment for marking comments from rachel
some overall comments

\documentclass[twocolumn,useAMS,usenatbib]{mn2e}
\usepackage{natbib}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{epsfig,graphicx}
\usepackage{subfig}
\usepackage{float}
\graphicspath{{Figures/}}
\topmargin-1cm

@@

@@

\author[Kannawadi et al.]
{Arun Kannawadi$^1$\thanks{\tt akannawa@andrew.cmu.edu}, 
Rachel Mandelbaum$^1$,
Claire Lackner$^2$, 
\\$^1$McWilliams center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
\\$^2$Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, the University of Tokyo, Kashiwa, Japan.
}

@@

\begin{keywords}

\end{keywords}

>>>>

\documentclass[twocolumn,useAMS,usenatbib]{mn2e}
\usepackage{natbib}
\usepackage{amsmath}
%\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{epsfig,graphicx}
\usepackage{subfig}
\usepackage{float}
\usepackage{color}
\graphicspath{{Figures/}}
\topmargin-1cm

@@

\newcommand{\rachel}[1]{{\textcolor{red}{#1}}}

@@

\author[Kannawadi et al.]
{Arun Kannawadi$^1$\thanks{\tt akannawa@andrew.cmu.edu}, 
Rachel Mandelbaum$^1$,
Claire Lackner$^2$, 
\\$^1$McWilliams Center for Cosmology, Carnegie Mellon University, Pittsburgh, PA 15217, USA
\\$^2$Kavli Institute for the Physics and Mathematics of the Universe (WPI), Todai Institutes for Advanced Study, the University of Tokyo, Kashiwa, Japan.
}

@@

\begin{keywords}
\rachel{You should choose up to 5 from the MNRAS keywords listing.}  
\end{keywords}

\rachel{The title is overly vague.  I recommend something like ``The
  impact of cosmic variance on simulating weak lensing surveys''.}

\rachel{Also, a question: we had given up on using \sersicn{} or \btt{}
  because the distributions have a complicated form including edge
  effects, but did you ever try looking at a simple statistic like the
  mean value?  i.e., just like your plots of the RMS ellipticity
  vs. redshift with different color points for over/underdense
  regions, except that you would plot $\langle n_s \rangle$ or
  $\langle B/T\rangle$.}

\rachel{Finally, it seems that some of your figure files have not been
  committed to the repository, because I do not see them.  Also I
  cannot compile everything, because the figures are a mix of PDF, PNG, and EPS.
I need either EPS to compile using latex, or PDF and PNG to compile
using pdflatex.}
